---
title: "A first look at the data"
author: "Simone D'Ambrogio"
subtitle: "Long Version"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: true
    toc: false
    toc_depth: 3
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, fig.align='left')
library(knitr)
## Global options
options(max.print="75")
opts_chunk$set(
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE
               )
opts_knit$set(width=75)
```

<style type="text/css">
  body {
    text-align: justify;
    font-size: 16px;
  }
  img[src$="centerme"] {
    display:block;
    margin: 0 auto;
  }
</style>

<br><br>

### Load libraries and dataset

```{r}

# Load libraries
library(dplyr); library(purrr); library(stringr)
library(ggplot2); library(ggpubr); library(jcolors)
library(cowplot)

# Load data
data_long <- readRDS('../Data/data_long.rds')$data

# ----- Mental Accounting ----- #
# Remove final questionnaires
data_long_MA <- data_long[, -(48:75)]
# Remove response time
idx_time      <- str_detect( names(data_long_MA),  'time_')
data_long_MA <- data_long_MA[, !idx_time]

```

<br><br>

### Scenario A: Mr. A vs Mr. B2

# {.tabset}

## 1

```{r A1, message=F, warning=F, fig.width=4, fig.height=5}
Q_A1 <- "Mr. A was given two tickets to the Regional 
lottery. He won $50 in one lottery 
and $25 in the other.
Mr. B was given a ticket to a single,
larger Regional lottery. He won $75.  
Who is happier?  \n"

data_long_MA %>% 
  ggplot(aes(A1, fill=as.factor(A1) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = Q_A1, y=NULL, x=NULL)

```

## 2

```{r A2, message=F, warning=F, fig.width=4, fig.height=5.5}

Q_A2 <- "Mr. A received a letter from the IRS saying
that he made a minor arithmetical mistake on
his tax return and owed $100. He received a
similar letter the same day from his state
income tax authority saying he owed $50. There
were no other repercussions from either mistake.

Mr. B received a letter from the IRS saying he
made a minor arithmetical mistake on his tax return
and owed $150. There were no other repercussions
from this mistake.

Who is more upset?\n"

data_long_MA %>%
  ggplot(aes(A2, fill=as.factor(A2) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = Q_A2, y=NULL, x=NULL)

```

## 3

```{r A3, message=F, warning=F, fig.width=4, fig.height=5}

Q_A3 <- "Mr. A bought his first National lottery
ticket and won $100. Also, in a freak accident,
he damaged the rug in his apartment and had
to pay the landlord $80.

Mr. B bought his first National lottery ticket
and won $20.

Who is happier?\n"

data_long_MA %>%
  ggplot( aes(A3_, fill=as.factor(A3_)) ) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = Q_A3,y=NULL, x=NULL)

```

## 4

```{r A4, message=F, warning=F, fig.width=4, fig.height=5}

Q_A4 <- "Mr. A’s car was damaged in a parking lot.
He had to spend $200 to repair the damage.
The same day the car was damaged, he 
won $25 in the office holiday raffle.

Mr. B’s car was damaged in a parking lot.
He had to spend $175 to repair the damage.

Who is more upset? \n"

data_long_MA %>%
  ggplot(aes(A4, fill=as.factor(A4) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = Q_A4,
       y=NULL, x=NULL)

```

# {-}

<br><br>

### Scenario B: The sold-out ticket scenario

# {.tabset}

## 1

```{r B1, message=F, warning=F, fig.width=8, fig.height=5}

Q_B1 <- "Imagine that you are going to a sold-out game of your favorite local sport-team, 
and you have an extra ticket to sell or give away. The price marked on the ticket is $5 but 
you were given your tickets for free by a friend. 

You get to the game early to make sure you get rid of the ticket. An informal survey of people 
selling tickets indicates that the going price is $5. You find someone who wants the ticket 
and takes out his wallet to pay you. He asks how much you want for the ticket. Assume that there 
is no law against charging a price higher than that marked on the ticket."

title <- ggdraw() + draw_label(Q_B1)

plot_b1_1 <- data.frame( resp = c(data_long_MA$B1_1_1, data_long_MA$B1_1_2),
            ques = c(rep('He is a friend',   50),
                     rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What price do you ask for if...") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = 'none')

plot_b2_1 <- data.frame( resp = c(data_long_MA$B2_1_1,
                                  data_long_MA$B2_1_2),
                         ques = c(rep('He is a friend',   50),
                                  rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What would you have said if you found out that\nthe going market price was $10 instead?") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8)) 
  # scale_x_continuous(breaks = seq(0, 20, 2), limits = c(-1,21))

plot_grid(title, plot_grid(plot_b1_1, plot_b2_1), ncol=1, rel_heights=c(0.6, 1))
```

## 2


```{r B2, message=F, warning=F, fig.width=8, fig.height=5}

Q_B2 <- "Imagine that you are going to a sold-out game of your favorite local sport-team, and 
you have an extra ticket to sell or give away. The price marked on the ticket is $5 but you 
were given your tickets for free by a friend. 

You get to the game early to make sure you get rid of the ticket. An informal survey of people 
selling tickets indicates that the going price is $5. You find someone who wants the ticket and 
takes out his wallet to pay you. He asks how much you want for the ticket. Assume that there is 
no law against charging a price higher than that marked on the ticket."

title <- ggdraw() + draw_label(Q_B2)

plot_b1_2 <- data.frame( resp = c(data_long_MA$B1_2_1,
                                  data_long_MA$B1_2_2),
                         ques = c(rep('He is a friend',   50),
                                  rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What price do you ask for if...") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = 'none') +
  scale_x_continuous(breaks = seq(0, 20, 2), limits = c(-1,21))

plot_b2_2 <- data.frame( resp = c(data_long_MA$B2_2__1,
                                  data_long_MA$B2_2__2),
                         ques = c(rep('He is a friend',   50),
                                  rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What would you have said if you found out that\nthe going market price was $10 instead?") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8)) +
  scale_x_continuous(breaks = seq(0, 20, 2), limits = c(-1,21))

plot_grid(title, plot_grid(plot_b1_2, plot_b2_2), ncol=1, rel_heights=c(0.6, 1))
```

## 3

```{r B3, message=F, warning=F, fig.width=8, fig.height=5}

Q_B3 <- "Imagine that you are going to a sold-out game of your favorite local sport-team, 
and you have an extra ticket to sell or give away. The price marked on the ticket is $5 but you 
paid $10 for each ticket when you bought them from another student. 

You get to the game early to make sure you get rid of the ticket. An informal survey of people 
selling tickets indicates that the going price is $5. You find someone who wants the ticket and 
takes out his wallet to pay you. He asks how much you want for the ticket. Assume that there is
no law against charging a price higher than that marked on the ticket."

plot_b1_3 <- data.frame( resp = c(data_long_MA$B1_3__1,
                                  data_long_MA$B1_3__2),
                         ques = c(rep('He is a friend',   50),
                                  rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What price do you ask for if...") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8)) +
  scale_x_continuous(breaks = seq(0, 20, 2), limits = c(-1,21))

plot_b2_3 <- data.frame( resp = c(data_long_MA$B2_3_1,
                                   data_long_MA$B2_3_2),
                          ques = c(rep('He is a friend',   50),
                                   rep('He is a stranger', 50))) %>%
  mutate(resp=as.numeric(resp)) %>%
  ggplot(aes(resp, fill=ques)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What would you have said if you found out that\nthe going market price was $10 instead?") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8)) +
  scale_x_continuous(breaks = seq(0, 20, 2), limits = c(-1,21))

plot_grid(title, plot_grid(plot_b1_3, plot_b2_3), ncol=1, rel_heights=c(0.6, 1))
```


# {-}


<br><br>

### Scenario C: Beer on the beach

# {.tabset}

## 1

```{r C1, message=F, warning=F, fig.width=10, fig.height=5}
Q_C1_1 <- "You are lying on the beach on a hot day. All you have to drink is ice water.
For the last hour you have been thinking about how much you would enjoy a nice cold 
bottle of your favourite brand of beer. A companion gets up to go make a call and offers
to bring back a beer from the only nearby place where beer is sold: a fancy resort hotel. 
They say that  the beer might be expensive and so ask how much you are willing to pay 
for the beer. They say that they will buy the beer if it costs as much or less than the 
price you state. But if it costs more than the price you state, they will not buy it. 
You trust your friend, and there is no possibility of bargaining with the bartender."

title <- ggdraw() + draw_label(Q_C1_1)

plot_c1_1 <- data_long_MA %>%
  mutate(resp=as.numeric(C1_1)) %>%
  ggplot(aes(resp)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What price do you tell them?") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8))

plot_grid(title, plot_grid(NULL, plot_c1_1, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.6, 1))
```

## 2

```{r C2, message=F, warning=F, fig.width=10, fig.height=5}

Q_C1_2 <- "You are lying on the beach on a hot day. All you have to drink is ice water. 
For the last hour you have been thinking about how much you would enjoy a nice cold bottle of 
your favourite brand of beer. A companion gets up to go make a call and offers to bring back a
beer from the only nearby place where beer is sold: a small, run-down grocery store. They say 
that the beer might be expensive and so ask how much you are willing to pay for the beer. 
They say that they will buy the beer if it costs as much or less than the price you state.
But if it costs more than the price you state, they will not buy it. You trust your friend, 
and there is no possibility of bargaining with the store owner."

title <- ggdraw() + draw_label(Q_C1_2)

plot_c1_2 <- data_long_MA %>%
  mutate(resp=as.numeric(C1_2)) %>%
  ggplot(aes(resp)) +
  geom_histogram(alpha=0.5) +
  theme_pubr() + labs(fill=NULL, x=NULL, y=NULL,
                      subtitle = "What price do you tell them?") +
  scale_fill_jcolors(palette = 'pal6') +
  theme(legend.position = c(0.8, 0.8))

plot_grid(title, plot_grid(NULL, plot_c1_2, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.6, 1))
```

# {-}


<br><br>

### Scenario D: Jacket-Calculator

# {.tabset}

## 1

```{r D1, message=F, warning=F, fig.width=10, fig.height=5}
Q_D1 <- "Imagine that you are about to purchase a jacket for $125 and a Bluetooth speaker for $15. 
The speaker salesman informs you that the speaker you wish to buy is on sale for $10 at the other 
branch of the store, located 20 minutes drive away."

title <- ggdraw() + draw_label(Q_D1)

plot_d2_1 <- data_long_MA %>%
  ggplot(aes(as.factor(D2_1), fill=as.factor(D2_1) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you make the trip to the other store?",
       y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_d2_1, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))
```

## 2

```{r D2, message=F, warning=F, fig.width=10, fig.height=5}

Q_D2 <- "Imagine that you are about to purchase a jacket for $15 and a Bluetooth speaker for $125. 
The speaker salesman informs you that the speaker you wish to buy is on sale for $120 at the other 
branch of the store, located 20 minutes drive away."

title <- ggdraw() + draw_label(Q_D2)

plot_d2_2 <- data_long_MA %>%
  ggplot(aes(as.factor(D2_2), fill=as.factor(D2_2) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you make the trip to the other store?",
       y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_d2_2, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))

```

## 3

```{r D3, message=F, warning=F, fig.width=10, fig.height=5}

Q_D3 <- "Imagine that you are about to purchase a jacket for $125 and a calculator for $15. 
The calculator salesman informs you that the calculator you wish to buy is on sale for $10 
at the other branch of the store, located 20 minutes drive away."

title <- ggdraw() + draw_label(Q_D3)

plot_d3 <- data_long_MA %>%
  ggplot(aes(as.factor(D3), fill=as.factor(D3) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you make the trip to the other store?",
       y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_d3, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))

```

## 4

```{r D4, message=F, warning=F, fig.width=10, fig.height=5}

Q_D4 <- "Imagine that you are about to purchase a jacket for $15 and a calculator for $125. 
The calculator salesman informs you that the calculator you wish to buy is on sale for $120 
at the other branch of the store, located 20 minutes drive away."

title <- ggdraw() + draw_label(Q_D4)

plot_d4 <- data_long_MA %>%
  ggplot(aes(as.factor(d4_), fill=as.factor(d4_) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you make the trip to the other store?",
       y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_d3, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))

```

# {-}

<br><br>

### Scenario E: Lost ticket

# {.tabset}

## 1

```{r E1, message=F, warning=F, fig.width=4, fig.height=5}
Q_E1 <- "Imagine you are on your way to a play
with a pair of tickets for which you have
paid $40. On entering the theater, you
discover that you have lost the tickets."

data_long_MA %>%
  ggplot(aes(as.factor(E1), fill=as.factor(E1) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you pay $40 for another pair of tickets?",
       title = Q_E1,
       y=NULL, x=NULL)
```

## 2

```{r E2, message=F, warning=F, fig.width=4, fig.height=5}
Q_E2 <- "Imagine you are on your way to a play,
with the intention of buying two tickets
worth $40 in total. On entering the
theater, you realize that you have lost
$40 in cash."

data_long_MA %>%
  ggplot(aes(as.factor(E2), fill=as.factor(E2) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none') +
  labs(subtitle = "Would you still pay $40 for a pair of tickets for the play?",
       title = Q_E2,
       y=NULL, x=NULL)

```

# {-}

<br><br>

### Scenario F: Membership gym

# {.tabset}

## 1

```{r F1, message=F, warning=F, fig.width=10, fig.height=5}

Q_F1 <- "Imagine that you have a membership to a gym in a nearby town that you travel to 
for business on a regular basis. You go to this gym exactly once a week: every Monday night 
when you’re in town. The membership allows you to pay $20 (non-refundable) per each visit. 
One Monday, just after you have arrived and changed, you receive a phone call that requires 
you to leave and forego your exercise that evening."

title <- ggdraw() + draw_label(Q_F1)

plot_f1 <- data_long_MA %>%
  ggplot(aes(as.factor(F1), fill=as.factor(F1) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 15, hjust=1)) +
  labs(subtitle = "How well does each of the following statements\ncapture your feelings about the cost of the missed workout?", y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_f1, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))

```

1: I feel like I just wasted $20, which is what I paid to work out that evening.

2: I feel like I wasted nothing, since my visit had already been paid for, and sometimes you just can’t take full advantage of things to which you are entitled.

3: I feel like I wasted something, perhaps time, perhaps money, but no specific amount or measure readily comes to mind.


## 2

```{r F2, message=F, warning=F, fig.width=10, fig.height=5}
Q_F2 <- "Imagine that you have a membership to a gym in a nearby town that you travel to for 
business on a regular basis. You go to this gym exactly once a week: every Monday night when 
you’re in town. The membership costs you $1000 a year (i.e., roughly $20 per visit). One Monday, 
just after you have arrived and changed, you receive a phone call that requires you to leave and
forego your exercise that evening."

title <- ggdraw() + draw_label(Q_F2)

plot_f2 <- data_long_MA %>%
  ggplot(aes(as.factor(F2), fill=as.factor(F2) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 15, hjust=1)) +
  labs(subtitle = "How well does each of the following statements capture\nyour feelings about the cost of the missed workout?", y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_f2, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.3, 1))

```

1: I feel like I just wasted $20, which is what I paid to work out that evening.

2: I feel like I wasted nothing, since my visit had already been paid for, and sometimes you just can’t take full advantage of things to which you are entitled.

3: I feel like I wasted something, perhaps time, perhaps money, but no specific amount or measure readily comes to mind.

# {-}

<br><br>

### Scenario G: Airplanes coupons scenario

# {.tabset}

## 1

```{r G1, message=F, warning=F, fig.width=10, fig.height=6}

Q_G1 <- "A number of airlines have recently introduced ‘‘upgrade coupons’’, which can be bought 
by anyone for $35 each and used to upgrade from economy to business-class on short-haul flights 
of up to 1000 miles (several coupons can be combined for longer flights). Suppose you are flying 
with a friend who has upgraded to business class and who is in possession of two additional such
coupons: one that he purchased for the standard price of $35, and another that he received from 
the airline as a free bonus. Just one coupon is required for upgrade on the current flight, and 
your friend offers you the coupon that he purchased so that you can upgrade as well, allowing 
you to sit together."

title <- ggdraw() + draw_label(Q_G1)

plot_g1 <- data_long_MA %>%
  ggplot(aes(as.factor(G1), fill=as.factor(G1) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 15, hjust=1)) +
  labs(subtitle = "What do you think is the most appropriate thing to do?", y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_g1, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.6, 1))
```

1: Pay your friend $35 for the coupon. <br>
2: Consider it a gift and not pay for the coupon. <br>
3: Pay some, but not the full amount for the coupon (for example, half the price). 

## 2

```{r G2, message=F, warning=F, fig.width=10, fig.height=6}
Q_G2 <- "A number of airlines have recently introduced ‘‘upgrade coupons’’, which can be 
bought by anyone for $35 each and used to upgrade from economy to business-class on short-haul
flights of up to 1000 miles (several coupons can be combined for longer flights). Suppose you 
are flying with a friend who has upgraded to business class and who is in possession of two 
additional such coupons: one that he purchased for the standard price of $35, and another that 
he received from the airline as a free bonus. Just one coupon is required for upgrade on the 
current flight, and your friend offers you the bonus coupon which he got for free so that you 
can upgrade as well, allowing you to sit together."

title <- ggdraw() + draw_label(Q_G2)

plot_g2 <- data_long_MA %>%
  ggplot(aes(as.factor(G2), fill=as.factor(G2) )) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_jcolors(palette = 'pal6') +
  theme_pubr() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 15, hjust=1)) +
  labs(subtitle = "What do you think is the most appropriate thing to do?", y=NULL, x=NULL)

plot_grid(title, plot_grid(NULL, plot_g2, NULL, nrow=1), 
          ncol=1, rel_heights=c(0.6, 1))

```

1: Pay your friend $35 for the coupon. <br>
2: Consider it a gift and not pay for the coupon. <br>
3: Pay some, but not the full amount for the coupon (for example, half the price). 

# {-}

<br><br>